Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-03-14 README.Rmd
update readme

This repository contains the data and code for my paper to be submitted to the Journal of Archaeological Science. Earlier versions were presented at the University of Cambridge [(2019)](https://github.com/benmarwick/March-2019-Cambridge-Big-Data-Archaeology) and New York University [(2025)](https://github.com/benmarwick/nyu-2025-workshop)

@@

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium from GitHub by clicking on the green `< > Code` button above, then click `Download ZIP`, and unzip on your computer
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to start the container on your computer
5. Go to http://localhost:8787/ with your browser and enter `rstudio` in both fields to start RStudio in your browser, running in the Docker container with all the required depedencies installed
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open the compendium's project
7. Run `rmarkdown::render("analysis/paper/paper.qmd")` to render the Quarto document that is the manuscript submitted for publication
8. When finished, to delete the Docker container from your computer, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`

>>>>

This repository contains the data and code for my paper that has been submitted to the _Journal of Archaeological Science_. Earlier versions were presented at the University of Cambridge [(2019)](https://github.com/benmarwick/March-2019-Cambridge-Big-Data-Archaeology) and New York University [(2025)](https://github.com/benmarwick/nyu-2025-workshop). A pre-print of the paper is online here and may be cited as follows:

> Marwick, B. (2025). Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science. Pre-print hosted at SocArXiv. Accessed 21 February 2025. https://doi.org/10.31235/osf.io/fdhvb_v1

@@

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium, e.g. from GitHub by clicking on the green `< > Code` button above, then click `Download ZIP`, then unzip on your computer
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to start the container on your computer
5. Go to http://localhost:8787/ with your browser and enter `rstudio` in both fields to start RStudio in your browser, running in the Docker container with all the required depedencies installed
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open the compendium's project
7. Run `rmarkdown::render("analysis/paper/paper.qmd")` to render the Quarto document that is the manuscript submitted for publication
8. When finished, to delete the Docker container from your computer, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`
